Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO$_2$ Reduction Reactions

### 2024-01-04 paper/main_sections/4.1_cnn_for_eads.tex
fix some broken symbols

\section{Adsorption energy prediction from electronic density of states with convolutional neural network}
Originating from the pioneering work of Hammer and Nørskov [30], the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.
To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity [31].
The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's \tau coefficient of -0.33, and followed by the vacuum level and electronegativity.
However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18, and therefore, refinements are imperative.
Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations [27, 32], the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy.
This finding also interpreted that in some reported prior studies, indicating that depending solely on the d-band center may be insufficient for accurate adsorption energy predictions in the context of SACs [33-37].
As a result, the development of a method tailored specifically for catalysts like SACs becomes essential.

>>>>

\section{Adsorption energy prediction from electronic density of states with convolutional neural network}
Originating from the pioneering work of Hammer and Nørskov [30], the d-band center model has emerged as a successful paradigm for employing descriptor to understand and predict the adsorption behavior on transition metal surfaces.
To investigate alternative electronic and elementary descriptors that may serve as more suitable substitutes for the d-band center model in the context of SACs, we performed Kendall rank correlation analysis to account for both linearity and non-linearity [31].
The correlation coefficient map, as presented in Figure 2a, highlighted the d-band center as the most informative descriptor with a Kendall's $\tau$ coefficient of -0.33, and followed by the vacuum level and electronegativity.
However, d-band center alone does not suffice for accurate predictions of intermediate adsorption energy as illustrated in the scatter plot Supplementary Figure 18, and therefore, refinements are imperative.
Unlike bulk transition metal surfaces, where the variations in the d-band centre account for the majority of the adsorption energy variations [27, 32], the unique structure of SACs introduces more variables rather than d-band center that are intrinsically correlated with the variations of adsorption energy.
This finding also interpreted that in some reported prior studies, indicating that depending solely on the d-band center may be insufficient for accurate adsorption energy predictions in the context of SACs [33-37].
As a result, the development of a method tailored specifically for catalysts like SACs becomes essential.

### 2024-01-04 paper/main_sections/4.2_volcano_plots.tex
fix some broken symbols

Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in Figure 3a and Supplementary Figure 11.
Given that HER is a key competing reaction with CO$_2$RR [44], we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
In adherence to Peterson and Nørskov's original framework [26], our choice of x and y axes descriptors aligned with Gads *CO and Gads *OH.
Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section.
Among the candidatures explored, Ge@g-C3N4 emerged as the most promising catalyst, demonstrating theoretical activity at a limiting potential of -1.2126 eV.
Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions.
The RDS volcano plot (Supplementary Figure 11) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at Gads *CO of 0.0589 eV and Gads *OH of -4.0075 eV, positioned at the right-center of the volcano plot.
Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO$_2$RR.
Consequently, it should be the focal point for future catalyst designs.
The activity and selectivity volcano plots imply that enhancing theoretical activity could be achieved by decreasing CO affinity while increasing OH affinity with the catalysts.
This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the “upright” configuration in *CO to the “horizontal” orientation in *CHO [45], and therefore facilitating dynamics and protonation of the *CO species.

>>>>

Expanding upon the revised scaling relations, we introduce an activity volcano plot and a rate-determining step (RDS) volcano plot for the CO$_2$RR process, shown in Figure 3a and Supplementary Figure 11.
Given that HER is a key competing reaction with CO$_2$RR [44], we also incorporated a selectivity volcano plot, presented in Supplementary Figure 12, to offer a comprehensive analysis of catalyst candidates.
In adherence to Peterson and Nørskov's original framework [26], our choice of x and y axes descriptors aligned with $\textit{G}_{\text{ads} \ast \text{CO}}$ and $\textit{G}_{\text{ads} \ast \text{OH}}$.
Further elaboration on how the limiting potentials were evaluated across the volcano plot can be found in the Methods section.
Among the candidatures explored, Ge@g-C3N4 emerged as the most promising catalyst, demonstrating theoretical activity at a limiting potential of -1.2126 eV.
Notably, the observed selectivity trend paralleled the activity trend, suggesting that catalysts exhibiting high theoretical activity are also resistant to HER side reactions.
The RDS volcano plot (Supplementary Figure 11) indicated protonation of *CO as the rate-determining step for nearly optimal candidates.
Moreover, the activity volcano plot predicted an optimal catalyst featuring a theoretical limiting potential of -1.0516 V, at $\textit{G}_{\text{ads} \ast \text{CO}}$ of 0.0589 eV and $\textit{G}_{\text{ads} \ast \text{OH}}$ of -4.0075 eV, positioned at the right-center of the volcano plot.
Results from RDS volcano plot indicate that protonation of *CO likely serves as the RDS for CO$_2$RR.
Consequently, it should be the focal point for future catalyst designs.
The activity and selectivity volcano plots imply that enhancing theoretical activity could be achieved by decreasing CO affinity while increasing OH affinity with the catalysts.
This result suggests a perspective: weak binding of CO to the catalyst surface might facilitate the rotation of C-O backbone from the “upright” configuration in *CO to the “horizontal” orientation in *CHO [45], and therefore facilitating dynamics and protonation of the *CO species.

### 2024-01-04 paper/main_sections/4.3_validation.tex
fix some broken symbols

To validate our method, we conducted occlusion experiments on Cr@g-C$_3$N$_4$, Co@g-C$_3$N$_4$ and Cu@g-C$_3$N$_4$.
Each of these supported metals possesses 3d subshells with different electronic configurations: half-filled, partially filled and fully filled, allowing us to test the universality of our approach.
The results of the occlusion experiment on the supported Cr single atom in Cr@g-C$_3$N$_4$ are given in Figure 4a.
The d_(x^2-y^2 ) orbital emerges as dominant in CO interaction.
Shielding electrons centered around -2 eV significantly alter the adsorption energy, indicating the potency of this orbital.
The real-space wavefunction visualization in Figure 4d corroborates these findings, highlighting the interaction between the d_(x^2-y^2) orbital of single metal atom and the adsorbate.
This suggests the d_(x^2-y^2) orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
Additionally, occlusion experiments were performed on the Co d_xy orbital of Co@g-C$_3$N$_4$ (Figure 4b) and the Cu d_xy orbital of Cu@g-C$_3$N$_4$ (Figure 4c).
In both cases, the d_xy orbital was identified as the dominant contributor.
While identifying the dominant orbital is crucial, these findings also suggest that interactions with adsorbates occurring out-of-plane are influenced by in-plane orbitals as well.
Importantly, it becomes evident that d orbitals do not universally impact interactions with adsorbates, emphasizing the need for case-specific discussions.

To validate the chemical relevance of predictions made by CNN model, we conducted COHP analysis, a theoretical bond-detecting tool used to identify bonding and anti-bonding contributions to band-structure energy [52].
In this research, interactions between the supported metal atom and atoms within a 5 Å radius were calculated to understand its bonding environment, as detailed in the Methods section.
The results of the occlusion experiment on the Co d_xy orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i.
The occlusion experiment pinpointed strong metal-adsorbate interactions at energy levels of -1 eV and -6.3 eV, which were confirmed by the COHP analysis.
We then investigated the non-dominant Co d_xz orbital, and the COHP analysis highlighted interactions at -1 eV and -6.5 eV, aligning with the findings from the occlusion experiments.

>>>>

To validate our method, we conducted occlusion experiments on Cr@g-C$_3$N$_4$, Co@g-C$_3$N$_4$ and Cu@g-C$_3$N$_4$.
Each of these supported metals possesses 3d subshells with different electronic configurations: half-filled, partially filled and fully filled, allowing us to test the universality of our approach.
The results of the occlusion experiment on the supported Cr single atom in Cr@g-C$_3$N$_4$ are given in Figure 4a.
The $d_{x^2-y^2}$ orbital emerges as dominant in CO interaction.
Shielding electrons centered around -2 eV significantly alter the adsorption energy, indicating the potency of this orbital.
The real-space wavefunction visualization in Figure 4d corroborates these findings, highlighting the interaction between the $d_{x^2-y^2}$ orbital of single metal atom and the adsorbate.
This suggests the $d_{x^2-y^2}$ orbital of supported Co predominantly influence the interaction with CO, and thus shielding electrons from this orbital markedly disturb the adsorption energy.
Additionally, occlusion experiments were performed on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$ (Figure 4b) and the $Cu d_xy$ orbital of Cu@g-C$_3$N$_4$ (Figure 4c).
In both cases, the $d_xy$ orbital was identified as the dominant contributor.
While identifying the dominant orbital is crucial, these findings also suggest that interactions with adsorbates occurring out-of-plane are influenced by in-plane orbitals as well.
Importantly, it becomes evident that d orbitals do not universally impact interactions with adsorbates, emphasizing the need for case-specific discussions.

To validate the chemical relevance of predictions made by CNN model, we conducted COHP analysis, a theoretical bond-detecting tool used to identify bonding and anti-bonding contributions to band-structure energy [52].
In this research, interactions between the supported metal atom and atoms within a 5 \AA(TODO: space missing) radius were calculated to understand its bonding environment, as detailed in the Methods section.
The results of the occlusion experiment on the Co $d_xy$ orbital of Co@g-C$_3$N$_4$, identified as the dominant orbital via occlusion experiments, were compared with the COHP analysis, as shown in Figure 4g and Figure 4i.
The occlusion experiment pinpointed strong metal-adsorbate interactions at energy levels of -1 eV and -6.3 eV, which were confirmed by the COHP analysis.
We then investigated the non-dominant Co $d_xz$ orbital, and the COHP analysis highlighted interactions at -1 eV and -6.5 eV, aligning with the findings from the occlusion experiments.

### 2024-01-04 paper/main_sections/4.4_shifting_exp.tex
fix some broken symbols

Shifting experiments for prediction of better catalysts.

While CNN models excel in prediction of the activity of catalyst candidates directly from eDOS, volcano plots point out directions leading to better catalysts. Exploring potential disturbances to adsorption energies and aiming to shift existing catalyst candidates closer to the peak of the activity volcano plot presents an intriguing avenue of investigation. In this work, we introduce an orbitalwise shifting experiment to explore the impact of orbitalwise eDOS shifting on adsorption behavior. The experiment involved shifting eDOS along the energy axis, and the CNN model was deployed to predict the resultant disturbance in adsorption energy for each shifting operation. Focusing on all Period 4 metal elements examined in this study, we analyzed the effects of eDOS shifting. To induce a moderate disturbance, we selected the energy range of -1 to 1 eV, and a shifting resolution of 0.005 eV/step was chosen to align with the eDOS calculation resolution.

Figure 5 illustrates that supported Ga and Ge, the sole p-block metals in our study, exhibited no response to d orbital shifting. This observation is consistent with their lack of d-electrons in their valence shells, reinforcing the reliability of our shifting experiments. We also investigated potential disturbance from p orbital shifting, as shown in Supplementary Figure 31 and found no significant response. This implies that Ge@g-C3N4 holds promise as a CO2RR electrocatalyst, given its high activity and resilience to electronic structure disturbances. Nevertheless, fine-tuning its performance through eDOS modulation might pose a challenge. In contrast, supported Fe, Cu and Zn display strong sensitivity to eDOS shifting. Interestingly, the adsorption energy consistently shifted towards more positive values, indicating a weakening of the catalyst-adsorbate interaction, regardless of the shifting direction within the investigated energy range. This underscores the intricate interplay between the supported metal atom and the substrate, emphasizing the necessity of a tool like the CNN model to predict such disturbances. Supported Cr exhibited a contrary response to eDOS shifting, strengthening the interaction with the CO adsorbate regardless of the shifting direction. Supported Ti, V, Co and Ni showed weak response to eDOS shifting, suggesting the need for alternative methods beyond manipulating their eDOS to regulate their interactions with CO adsorbate.

>>>>

% Results and Discussion Part Four: Shifting experiments for prediction of better catalysts

\section{Validation of CNN predictions}
While CNN models excel in prediction of the activity of catalyst candidates directly from eDOS, volcano plots point out directions leading to better catalysts.
Exploring potential disturbances to adsorption energies and aiming to shift existing catalyst candidates closer to the peak of the activity volcano plot presents an intriguing avenue of investigation.
In this work, we introduce an orbitalwise shifting experiment to explore the impact of orbitalwise eDOS shifting on adsorption behavior.
The experiment involved shifting eDOS along the energy axis, and the CNN model was deployed to predict the resultant disturbance in adsorption energy for each shifting operation.
Focusing on all Period 4 metal elements examined in this study, we analyzed the effects of eDOS shifting.
To induce a moderate disturbance, we selected the energy range of -1 to 1 eV, and a shifting resolution of 0.005 eV/step was chosen to align with the eDOS calculation resolution.

Figure 5 illustrates that supported Ga and Ge, the sole p-block metals in our study, exhibited no response to d orbital shifting.
This observation is consistent with their lack of d-electrons in their valence shells, reinforcing the reliability of our shifting experiments.
We also investigated potential disturbance from p orbital shifting, as shown in Supplementary Figure 31 and found no significant response.
This implies that Ge@g-C$_3$N$_4$ holds promise as a CO$_2$RR electrocatalyst, given its high activity and resilience to electronic structure disturbances.
Nevertheless, fine-tuning its performance through eDOS modulation might pose a challenge.
In contrast, supported Fe, Cu and Zn display strong sensitivity to eDOS shifting.
Interestingly, the adsorption energy consistently shifted towards more positive values, indicating a weakening of the catalyst-adsorbate interaction, regardless of the shifting direction within the investigated energy range.
This underscores the intricate interplay between the supported metal atom and the substrate, emphasizing the necessity of a tool like the CNN model to predict such disturbances.
Supported Cr exhibited a contrary response to eDOS shifting, strengthening the interaction with the CO adsorbate regardless of the shifting direction.
Supported Ti, V, Co and Ni showed weak response to eDOS shifting, suggesting the need for alternative methods beyond manipulating their eDOS to regulate their interactions with CO adsorbate.

### 2024-01-04 paper/main_sections/5_methods.tex
fix some broken symbols

Methods
DFT calculations.
# TODO: fix multiply sign (×)
Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 [53-55] to optimize geometries and determine the electronic structure. The Perdew-Burke-Ernzerhof (PBE) functional [53] within the generalized gradient approximation (GGA) [56] was utilized to describe the electron-ion interactions and electronic exchange correlations. Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV. Geometry optimizations were performed using Γ-Centered K-point meshes of (2 × 2 × 1) until the force on each atom fell below 0.02 eV Å-1. Electronic structure calculations utilized denser K-point meshes of (3 × 3 × 1) and employed self-consistent field (SCF) methods.

Catalyst models.
Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C3N4), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C2N. The specific single metal atoms studied are outlined in Supplementary Figure 1. To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 Å were introduced.

CO2RR pathway.
The C1 production CO2RR pathway, as initially described by Peterson et al. [45] and later confirmed by Jiao et al. [57] for g-C3N4 based SACs, involves the following elementary steps. Asterisks (*) indicate species adsorbed on the SAC surfaces:
# TODO: check format
% (CO_2+ ^*+H^++e^- □(→┴(          ) )  ^* COOH#(1))
% ( ^* COOH+H^++e^- □(→┴(          ) )  ^* CO+H_2 O#(2))
% ( ^* CO+H^++e^- □(→┴(          ) )  ^* CHO#(3)######)
% ( ^* CHO+H^++e^- □(→┴(          ) )  ^* CH_2 O#(4)##)
% ( ^* CH_2 O+H^++e^- □(→┴(          ) )  ^* OCH_3#(5)#)
% ( ^* OCH_3+H^++e^- □(→┴(          ) )  ^* O+CH_4#(6)#)
% ( ^* O+H^++e^- □(→┴(          ) )  ^* OH#(7)#)
% ( ^* OH+H^++e^- □(→┴(          ) )  ^*+H_2 O#(8)#)

Free energy calculations.
Free energies were computed from electronic energies by considering thermal corrections, incorporating normal mode analysis of all degrees of freedom of adsorbates. The free energy G was calculated using the formula:
# TODO: check format
% (G=E+ E_ZPE-TS#(9))
where G represents the free energy, E denotes electronic energy, EZPE is the zero-point energy, T represents temperature in Kevin, and S stands for entropy. Detailed information regarding these corrections can be found in Supplementary Section 1.3.

The computational hydrogen electrode (CHE) model [45, 58] was employed to introduce potential dependence. At the reference electrode surface, the reaction
# TODO: check format
% (1/2 H_2(g)   □(↔┴(           )  H^++ e^- )#(10))
is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
% (μ(H^+)+μ(e^-)=1/2 μ(H_2(g) )-eU#(11))
For the external potential U applied, the change in free energy (ΔG) was determined using the equation:
% (∆G_n (U)= ∆G_n (U=0)+neU#(12))
Here, μ represents chemical potential, U signifies the external potential applied, n represents the number of proton-electron pairs transferred, and e denotes the elementary charge.

Hybrid descriptor for volcano plots.
Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 and Supplementary Table 13. Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
# TODO: check format
(G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
Here, θ represents the mixing ratio of the CO descriptor, Z denotes any adsorbate, and k and cZ are adsorbate-specific scaling parameters. The optimal mixing ratio θ is determined through iterative exploration across the range, utilizing a step length of 0.01.

@@

Consequently, the limiting potential UL is entirely determined by two descriptors through the following equation:
# TODO: check format
% (U_L=-max⁡{〖ΔG〗_i }/e#(15)#)
Where ∆Gi represents the free energy change of reaction step i.

This approach simplifies the theoretical performance assessment of any catalyst within the scope of our research to only two descriptors: G_ads CO and G_ads OH. This method offers a visual representation of the high-dimensional optimization challenge. To aid visualization, a 2D mesh grid is established, enabling vectorized assessments of limiting potentials across the descriptor value ranges. At each grid point, the limiting potential is computed using Equation 16.

CNN architecture and hyperparameter tuning.
We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification [59], as illustrated in Figure 2b and 2c. This multi-branched CNN comprises nine branches tailored to handle eDOS orbitals while ensuring a reduced memory footprint.

@@

Data augmentation and CNN model training.
To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space [61], we applied data augmentation techniques to the initial dataset using the following procedures:
	In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 Å above the supported single metal atom, five intermediate images were interpolated. These images were distributed between the initial and final states at a spacing of 0.5 Å, starting from the initial state side.
	A diverse set of smearing techniques was employed to determine of partial occupancies fnk, including the tetrahedron method [62] and the Gaussian method. For the Gaussian method, the smearing width was varied within the range of 0.01 eV to 0.1 eV. This careful selection of methods was made to guarantee reliable and consistent predictions of adsorption energies from the model, regardless of the smearing technique used.
The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 and a variance of 3.2821. Twenty pecent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.

Occlusion experiments.
Supplementary Figure 21 visually illustrates the occlusion experiment methodology. To maintain consistent shapes, zero-padding was applied to the input eDOS arrays. Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions. Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary Section 2.6. Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.

Shifting experiments.
Supplementary Figure 30 illustrates the implemented shifting experiment protocol. In this study, the initial electronic density of states underwent controlled shifting along the energy axis. This protocol ranges from -1 eV to 1 eV, with a step length of 0.005 eV per image. To maintain a uniform energy window, each image underwent cropping and padding procedures. The resulted output arrays took the form of [400, 1] arrays for simultaneous orbital shifting and [400, 9] arrays for individual orbital shifting. The energy range for shifting was chosen to induce a moderate disturbance to adsorption energy.

Chemical bond analysis and real-space wavefunction visualization.
COHP analysis was performed using the Local-Orbital Basis Suite Towards Electronic-Structure Reconstruction (LOBSTER) package  [52, 63-66] version 4.1.0, with the GGA-PBE wavefunctions fitted by S. Maintz [63, 67]. A Gaussian smearing for energy integration was employed with a broadening width of 0.05 eV. The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 Å to 5.0 Å from the single metal atom. Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT [68] and VESTA [69].

Machine learning and data analysis environment.
The CNN model was implemented using TensorFlow [70], and hyperparameter optimization was conducted using the Hyperband [60] algorithm via KerasTuner [71]. For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary Section 3.

>>>>

% Methods

\section{Methods}

\subsection{DFT calculations}
# TODO: fix multiply sign (×)
Spin-polarized density functional theory calculations were performed using the Vienna Ab initio Simulation Package (VASP) version 5.4.4 [53-55] to optimize geometries and determine the electronic structure.
The Perdew-Burke-Ernzerhof (PBE) functional [53] within the generalized gradient approximation (GGA) [56] was utilized to describe the electron-ion interactions and electronic exchange correlations.
Kohn-Shan equations were approached employing a plane-wave basis set with a cut-off energy of 440 eV.
Geometry optimizations were performed using Γ-Centered K-point meshes of (2 × 2 × 1) until the force on each atom fell below 0.02 eV Å-1 (TODO:).
Electronic structure calculations utilized denser K-point meshes of (3 × 3 × 1) and employed self-consistent field (SCF) methods.

\subsection{Catalyst models}
Supported SACs were modelled by anchoring individual metal atoms onto various 2D substrates, including graphitic carbon nitride (g-C$_3$N$_4$), nitrogen-doped graphene, graphene with dual-vacancy, black phosphorous, boron nitride, and monolayer C$_2$N.
The specific single metal atoms studied are outlined in Supplementary Figure 1.
To prevent interactions between adjacent images along the z-axis, vacuum layers of 15 Å (TODO:) were introduced.

\subsection{CO$_2$RR pathway}
The C1 production CO$_2$RR pathway, as initially described by Peterson et al. [45] and later confirmed by Jiao et al. [57] for g-C$_3$N$_4$ based SACs, involves the following elementary steps.
Asterisks (*) indicate species adsorbed on the SAC surfaces:
# TODO: check format
% (CO_2+ ^*+H^++e^- □(→┴(          ) )  ^* COOH#(1))
% ( ^* COOH+H^++e^- □(→┴(          ) )  ^* CO+H_2 O#(2))
% ( ^* CO+H^++e^- □(→┴(          ) )  ^* CHO#(3)######)
% ( ^* CHO+H^++e^- □(→┴(          ) )  ^* CH_2 O#(4)##)
% ( ^* CH_2 O+H^++e^- □(→┴(          ) )  ^* OCH_3#(5)#)
% ( ^* OCH_3+H^++e^- □(→┴(          ) )  ^* O+CH_4#(6)#)
% ( ^* O+H^++e^- □(→┴(          ) )  ^* OH#(7)#)
% ( ^* OH+H^++e^- □(→┴(          ) )  ^*+H_2 O#(8)#)

\subsection{Free energy calculations}
Free energies were computed from electronic energies by considering thermal corrections, incorporating normal mode analysis of all degrees of freedom of adsorbates.
The free energy $\textit{G}$ was calculated using the formula:
# TODO: check format
% (G=E+ E_ZPE-TS#(9))
where $\textit{G}$ represents the free energy, $\textit{E}$ denotes electronic energy, $\textit{E}_{\text{ZPE}}$ is the zero-point energy, $\textit{T}$ represents temperature in Kevin, and $\textit{S}$ stands for entropy.
Detailed information regarding these corrections can be found in Supplementary Section 1.3.

The computational hydrogen electrode (CHE) model [45, 58] was employed to introduce potential dependence.
At the reference electrode surface, the reaction
# TODO: check format
% (1/2 H_2(g)   □(↔┴(           )  H^++ e^- )#(10))
is in equilibrium, allowing the calculation of the chemical potential of the electron-proton pair as:
% (μ(H^+)+μ(e^-)=1/2 μ(H_2(g) )-eU#(11))
For the external potential $\textit{U}$ applied, the change in free energy ($\Delta \textit{G}$) was determined using the equation:
% (∆G_n (U)= ∆G_n (U=0)+neU#(12))
Here, $\mu$ represents chemical potential, $\textit{U}$ signifies the external potential applied, $\textit{n}$ represents the number of proton-electron pairs transferred, and $\textit{e}$ denotes the elementary charge.

\subsection{Hybrid descriptor for volcano plots}
Hybrid descriptors incorporate both descriptors within a single equation, enhancing the accuracy of scaling relationship with minimal computational overhead, as demonstrated in Supplementary Figure 10 and Supplementary Table 13.
Comprehensive analyses are presented Supplementary Section 1.5. This leads to the formulation of the scaling relation:
# TODO: check format
% (G_ads Z=k[θ*G_ads CO+(1-θ)*G_ads OH]+c_Z#(13)##)
Here, $\theta$ represents the mixing ratio of the CO descriptor, $\textit{Z}$ denotes any adsorbate, and $\textit{k}$ and $\textit{c}_{Z}$ are adsorbate-specific scaling parameters.
The optimal mixing ratio $\theta$ is determined through iterative exploration across the range, utilizing a step length of 0.01.

@@

Consequently, the limiting potential $\textit{U}_{L}$ is entirely determined by two descriptors through the following equation:
# TODO: check format
% (U_L=-max⁡{〖ΔG〗_i }/e#(15)#)
Where ∆Gi represents the free energy change of reaction step i.

This approach simplifies the theoretical performance assessment of any catalyst within the scope of our research to only two descriptors: $G_{\textit{ads} \, \textit{CO}}$ and $G_{\textit{ads} \, \textit{OH}}$.
This method offers a visual representation of the high-dimensional optimization challenge.
To aid visualization, a 2D mesh grid is established, enabling vectorized assessments of limiting potentials across the descriptor value ranges.
At each grid point, the limiting potential is computed using Equation 16.

\subsection{CNN architecture and hyperparameter tuning}
We designed our CNN architecture drawing inspiration from its successful implementation in tasks involving electrocardiogram signal classification [59], as illustrated in Figure 2b and 2c.
This multi-branched CNN comprises nine branches tailored to handle eDOS orbitals while ensuring a reduced memory footprint.

@@

\subsection{Data augmentation and CNN model training}
To enhance the generalizability and robustness of the our CNN model, and achieve comprehensive coverage of the chemical space [61], we applied data augmentation techniques to the initial dataset using the following procedures:
	- In addition to the designated "initial state" of the adsorption process, where the adsorbate positioned 6.5 Å (TODO:) above the supported single metal atom, five intermediate images were interpolated. These images were distributed between the initial and final states at a spacing of 0.5 Å (TODO:), starting from the initial state side.
	- A diverse set of smearing techniques was employed to determine of partial occupancies $f_{nk}$, including the tetrahedron method [62] and the Gaussian method. For the Gaussian method, the smearing width was varied within the range of 0.01 eV to 0.1 eV. This careful selection of methods was made to guarantee reliable and consistent predictions of adsorption energies from the model, regardless of the smearing technique used.

The augmented dataset comprises 12,312 samples, with adsorption energies having a standard deviation of 1.8117 and a variance of 3.2821.
Twenty pecent of these samples were allocated to the validation set. Throughout the training process, a batch size of 64 was employed to ensure a balanced learning dynamic.

\subsection{Occlusion experiments}
Supplementary Figure 21 visually illustrates the occlusion experiment methodology. To maintain consistent shapes, zero-padding was applied to the input eDOS arrays.
Focusing on understanding the influence of metals on adsorption behavior, a masker with dimensions [width, 1, 1] was employed along the metal channel to eliminate cross-orbital interactions.
Here, "width" denotes the masker width, and detailed explanations for determining the width are provided in Supplementary Section 2.6.
Through recursive application of these maskers, variations in predicted adsorption energies from the CNN model were recorded, generating an occlusion array.

\subsection{Shifting experiments}
Supplementary Figure 30 illustrates the implemented shifting experiment protocol.
In this study, the initial electronic density of states underwent controlled shifting along the energy axis.
This protocol ranges from -1 eV to 1 eV, with a step length of 0.005 eV per image.
To maintain a uniform energy window, each image underwent cropping and padding procedures.
The resulted output arrays took the form of [400, 1] arrays for simultaneous orbital shifting and [400, 9] arrays for individual orbital shifting.
The energy range for shifting was chosen to induce a moderate disturbance to adsorption energy.

\subsection{Chemical bond analysis and real-space wavefunction visualization}
COHP analysis was performed using the Local-Orbital Basis Suite Towards Electronic-Structure Reconstruction (LOBSTER) package  [52, 63-66] version 4.1.0, with the GGA-PBE wavefunctions fitted by S. Maintz [63, 67].
A Gaussian smearing for energy integration was employed with a broadening width of 0.05 eV.
The quantification of bonding strength between the single metal atom and the substrate was achieved through the summation of interactions with neighboring atoms within a range of 0.5 Å (TODO:) to 5.0 Å (TODO:) from the single metal atom.
Orbitals of interest were confirmed through band-structure analysis, and real-space wavefunctions were subsequently visualized using VASPKIT [68] and VESTA [69].

\subsection{Machine learning and data analysis environment}
The CNN model was implemented using TensorFlow [70], and hyperparameter optimization was conducted using the Hyperband [60] algorithm via KerasTuner [71].
For a more detailed overview of our machine learning setup and data analysis environment, please refer to Supplementary Section 3.

### 2024-01-04 paper/main_sections/6_tail.tex
fix some broken symbols

Data Availability
Essential source data required to replicate the study's results–including VASP input files, structure files of SACs, eDOS arrays and the pretrained CNN model–are available on GitHub at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request. Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.

Code Availability
Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos or obtained from the corresponding authors upon request.

Acknowledgements
The QUT eResearch Office provided computational resources and services used in this work. This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), supported by the Australian Government. It was also supported by resources provided by the Pawsey Supercomputing Research Centre with funding from the Australian Government and the Government of Western Australia. Insights into deep learning methodologies were contributed by Mr. Yanwei Guan from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT. The machine learning and data analysis implementation benefited from resources provided by the GitHub, TensorFlow and Stack Overflow communities. Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on Crystal Orbital Hamilton Population analysis.

Author Contributions
H.Y. performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript. J.Z. engaged in valuable discussions on DFT calculations. Q.W. provided advice on the computer code revisions. W.L. facilitated resource acquisition and offered research supervision. B.L. provided guidance on DFT calculations and offered research supervision. Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research. T.L. guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.

Competing interests
The authors declare no competing interests in relation to this research.

>>>>

% Data/Code Availability, Acknowledgements, Author Contributions and Competing Interests

\section{Tail}

\subsection{Data Availability}
Essential source data required to replicate the study's results-including VASP input files,
structure files of SACs, eDOS arrays and the pretrained CNN model-are available on GitHub
at https://github.com/DanielYang59/cnn4dos or can be provided by the corresponding authors upon request.
Due to their substantial size in terabytes, the complete source data is not currently hosted on publicly available repositories but can also be obtained from the corresponding authors upon request.

\subsection{Code Availability}
Associated computer code for this study can be accessed on GitHub at https://github.com/DanielYang59/cnn4dos, or obtained from the corresponding authors upon request.

 \subsection{Acknowledgements}
The QUT eResearch Office provided computational resources and services used in this work.
This research was undertaken with the assistance of resources and services from the National Computational Infrastructure (NCI), supported by the Australian Government.
It was also supported by resources provided by the Pawsey Supercomputing Research Centre with funding from the Australian Government and the Government of Western Australia.
Insights into deep learning methodologies were contributed by Mr. Yanwei Guan from Chongqing University and Mr. Zhipeng He from Assoc. Prof. Chun Ouyang's team at QUT.
The machine learning and data analysis implementation benefited from resources provided by the GitHub, TensorFlow and Stack Overflow communities.
Dr. Ryky Nelson from RWTH Aachen University offered valuable guidance on Crystal Orbital Hamilton Population analysis.

\subsection{Author Contributions}
H.Y. performed DFT calculations, implemented Python code the machine learning methodologies and data analysis, and drafted and refined the manuscript.
J.Z. engaged in valuable discussions on DFT calculations.
Q.W. provided advice on the computer code revisions.
W.L. facilitated resource acquisition and offered research supervision.
B.L. provided guidance on DFT calculations and offered research supervision.
Z.S. initiated the research concept, contributed to manuscript revisions, and supervised the overall research.
T.L. guided DFT calculations and data analysis, offering continuous supervision throughout the research and manuscript drafting.

\subsection{Competing Interests}
The authors declare no competing interests in relation to this research.
